Verifying Spatial Properties of Array Computations

### 2017-04-18 oopsla17/evaluation.tex
new run and tickLHSvar wording

We would not expect to infer a stencil for each array statement we
found because our analysis restricts the array-subscript-statements
that we classify as a stencil. In fact, we were able to infer a
stencil from \overalltickAssignSuccessPercentOfTickAssign\% of these
statements. A single statement can involve multiple arrays and we
ended up with \num{\overallnumStencilSpecs} specifications. This shows
that we can express a large number of stencil shapes within our
high-level abstraction and validates our initial hypothesis that many
stencil computations have a regular shape.

>>>>

We would not expect to infer a stencil for each array statement we
found because our analysis restricts the array-subscript-statements
that we classify as a stencil. For example, \num{\overalltickLHSvar}
potential stencils were discarded because the left-hand side was not
an array access. Overall, we were able to infer a stencil from
\overalltickAssignSuccessPercentOfTickAssign\% of the statements
involving an array assignment. A single statement can involve multiple
arrays and we ended up with \num{\overallnumStencilSpecs}
specifications. This shows that we can express a large number of
stencil shapes within our high-level abstraction and validates our
initial hypothesis that many stencil computations have a regular
shape.
